The role of motor inhibition during covert speech production

### 2021-10-26 manuscript.tex
incorporating feedback from co-authors

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Create explanation Box environment %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{Nalborczyk {et~al.}} %use et al only if is more than 1 author
\def\Authors{Ladislas Nalborczyk\,$^{1,2,*}$, Ursula Debarnot\,$^{3,4}$, Marieke Longcamp\,$^{2}$, Aymeric Guillot\,$^{3,4}$, and F.-Xavier Alario\,$^{1}$}
% Affiliations should be keyed to the author's name with superscript numbers and be listed as follows: Laboratory, Institute, Department, Organization, City, State abbreviation (USA, Canada, Australia), and Country (without detailed address information such as city zip codes or street names).
% If one of the authors has a change of address, list the new address below the correspondence details using a superscript symbol and use the same symbol to indicate the author in the author list.
\def\Address{$^{1}$Aix Marseille Univ, CNRS, LPC, Marseille, France \\
$^{2}$Aix Marseille Univ, CNRS, LNC, Marseille, France \\
$^{3}$Inter-University Laboratory of Human Movement Biology-EA 7424, University of Lyon, University Claude Bernard Lyon 1, Villeurbanne, France \\
$^{4}$Institut Universitaire de France, Paris, France}
% The Corresponding Author should be marked with an asterisk
% Provide the exact contact address (this time including street name and city zip code) and email of the corresponding author
\def\corrAuthor{Ladislas Nalborczyk}
\def\corrEmail{ladislas.nalborczyk@univ-amu.fr}

@@

% Alternative title: Does covert speech production imply the motor inhibition of overt speech acts?

@@

% One of the most influential theoretical model of motor imagery the motor simulation theory \cite{jeannerod_origin_2006, jeannerod_representing_1994, jeannerod_neural_2001}, postulates the existence of a continuum between the covert and the overt execution of an action and that action representations can operate off-line via a simulation mechanism. In short, covert actions would rely on the same set of mechanisms as the overt actions they simulate, except that execution is inhibited \citep{oshea_does_2017}. A second class of models are concerned with the phenomenon of emulation \citep{grush_emulation_2004} and with internal models \cite[for a review of the similarities and dissimilarities between simulation and emulation models, see][]{gentsch_towards_2016}. Internal model theories share the postulate that action control uses internal models, that is, systems that simulate the behaviour of the motor apparatus \citep[e.g.,][]{jordan_forward_1992, kawato_hierarchical_1987}. The function of internal models is to estimate and anticipate the outcome of a motor command. Among the internal model theories, motor control models based on robotic principles \citep[e.g.,][]{kawato_internal_1999, wolpert_internal_1995} assume two kinds of internal models: a forward model (or simulator) that predicts the sensory consequences of motor commands from efference copies of the issued motor commands, and an inverse model (or controller) that calculates the feedforward motor commands from the desired sensory states \citep{gentsch_towards_2016, loevenbruck_cognitive_2018}. Notice that in the following, we do not distinguish further between simulation and emulation, and we use these terms interchangeably to designate the mechanism through which sensory consequences of motor commands (or copy thereof) are computed by forward internal models.

% By building upon models of speech motor control (e.g., Houde \& Nagarajan, 2011; Wolpert et al., 1995), a recent model describes wilful (voluntary) expanded covert speech as "multi-modal acts with multi-sensory percepts stemming from coarse multi-sensory goals" \cite{loevenbruck_cognitive_2018}. In other words, this model considers the auditory and kinaesthetic sensations perceived during covert speech to be the predicted sensory consequences of inhibited speech motor acts, emulated by internal forward models that use the efference copies issued from an inverse model (this proposal shares some similarities with the emulation model of motor imagery, Grush, 2004) \cite{grush_emulation_2004}. This model is supported by several empirical results providing both behavioural and neurophysiological evidence for the efference copies issued during inner speech production (e.g., Scott, 2013; Whitford et al., 2017)...

@@

First and foremost, we need to make a distinction between at least two different types of inhibition: the inhibition of physical response (e.g., planning to raise the arm and finally not doing it), and cognitive inhibition, defined as "the stopping or overriding of a mental process, in whole or in part, with or without intention" \citep{gorfein_concept_2007}. Here, we are concerned with the former, which can be defined broadly as the withholding, suppression, or overriding of an inappropriate, prepotent, or unwanted motor response \citep{aron_neural_2007, oshea_go_2018}. To be more precise, \cite{ridderinkhof_dont_2014} described the concept of response inhibition on three continuous dimensions: intentionality, premeditation, and specificity. Inhibition can be employed with more or less intentionality (intentional vs. reactive), planned ahead or employed in the moment (early vs. late inhibition), and applied to a specific action and effector, or more globally, that is, to all actions and/or effectors.

Crucially, we hypothesise that covert speech involves an intentional (we know we want to produce these actions covertly rather than overtly) but automatic (we do not explicitly think about not producing movements), planned ahead, and possibly global form of response inhibition. Notice however that the type of motor inhibition that may be at play during motor imagery is still different from the "proactive inhibition" in the motor inhibition literature. Indeed, in behavioural tasks aiming to assess proactive inhibition, participants are instructed no to execute an action. In contrast, while doing motor imagery,
participants are asked to produce the action \textit{covertly}, which implicitly implies that it should not be executed overtly \citep{guillot_imagining_2012}. Using an action mode (overt vs. covert) switching paradigm, \cite{rieger_inhibition_2017} and \cite{bart_inhibitory_2021} have showed that the motor imagery of hand movements is accompanied by both global and effector-specific inhibition \citep[these results were also replicated in][]{scheil_motor_2018}.

% further confirmed that both global and effector-specific inhibition may be at play during imagined (hand) movements and suggested that these two types of inhibition may work together and compensate for each other... \cite{schwoebel_man_2002}...

After reviewing evidence from electrophysiological, neuroimaging, and clinical studies, \cite{guillot_imagining_2012} suggested three possible routes whereby motor commands can be inhibited during motor imagery. First, motor inhibition can be integrated within the representation of the action to be produced internally, therefore no inhibition would be involved during motor imagery. Second, cerebral regions such as the supplementary motor area (SMA) \citep{kasess_suppressive_2008} or the right inferior frontal gyrus (rIFG) may weaken the motor commands that are emitted during motor imagery \citep[e.g.,][]{angelini_motor_2015, angelini_proactive_2016}, in addition to modulations of short-interval intracortical inhibition within the primary motor cortex itself \citep{neige_unravelling_2020}. More precisely, the pre-SMA and the rIFG may work together to intercept the action process via the basal ganglia (subthalamic nucleus, STN), hence suppressing the output from the basal ganglia which in turn might inhibit the primary motor cortex \citep{aron_reactive_2011} (cf. Figure \ref{fig:2}).\footnote{\cite{diesburg_pause-then-cancel_2021} proposed a functional dissociation between the pre-SMA and the rIFC in a two-stage "pause-then-cancel" model of action inhibition. In their model, they suggest that the pre-SMA would be involved in (globally) pausing the action whereas the rIFC would be involved in selectively cancelling (resetting) motor commands. Whether this functional dissociation is preserved in motor imagery remains an open question.} Third, downstream regions in the cerebellum \citep[e.g.,][]{lotze_activation_1999}, in the brainstem \citep[e.g.,][]{jeannerod_neural_2001, jeannerod_motor_2006}, or at the spinal level may contribute to motor inhibition at a later stage.

The role of inhibitory mechanisms during motor imagery and covert speech could be assessed in several ways. First, it could be assessed by experimentally manipulating the activity of the inhibitory network responsible for preventing execution during motor imagery. For instance, transcranial magnetic stimulation (TMS) could be used to "brake" these inhibitory mechanisms and "force" or facilitate execution during motor imagery \citep[e.g.,][]{angelini_motor_2015, angelini_proactive_2016}. Second, the role of inhibitory mechanisms during covert verbal actions could be examined in a population with well-identified inhibitory deficits. For instance, Tourette syndrome is a childhood-onset neurological disorder affecting approximately 1\% of children and characterised by chronic motor and phonic tics \citep{jackson_inhibition_2015}. Verbal tics can consist of repeating sounds, words, or utterances (palilalia), producing inappropriate or obscene utterances (coprolalia), or the repetition of another’s words (echolalia). \cite{ganos_action_2014} have showed that the behavioural performance during a stop-signal reaction-time task was similar across Tourette patients and healthy controls. In their review, \cite{jackson_inhibition_2015} suggested that increased control over motor outputs is brought by local increases in GABAergic "tonic" inhibition within regions such as the SMA, leading to localised reductions in the gain of motor excitability. For these reasons, comparing the neural implementation of inhibitory mechanisms during covert speech in patients with Tourette syndrome and healthy controls may shed light on the role and flexibility of these mechanisms.

@@

@@

\cite{watson_psychology_1919} suggested that thought (i.e., covert speech, in his terminology) was rooted in (overt) speech, that is, that covert speech matures from overt speech. \cite{vygotsky_thought_1934} further formulated the idea that covert speech originates from private egocentric speech, that is, self-addressed overt speech in childhood. In other words, Vygotsky observed, as Piaget before, that egocentric speech tends to be internalised during child development. \cite{fernyhough_alien_2004} extended this idea with four levels of internalisation: external dialogue, private speech, expanded inner speech and condensed inner speech. These levels represent stages of development but also define movements between levels, that is, how we go from overt to covert speech and conversely. The level at which speech is expressed may depend on inhibitory control applied at different levels in the production flow, such as the formulation or the articulatory planning level \citep{grandchamp_condialint_2019}. Therefore, producing speech covertly crucially depends on successfully inhibiting speech production at several levels. We formulate the hypothesis that the progressive internalisation of speech during childhood may be related to the development of inhibitory abilities.

@@

% This is consistent with results from training studies suggesting that we rely more and more on domain-general (e.g., memory-based) processes with expertise (e.g., Tarr and Pinker, 1989;Jolicoeur, 1985)

Second, the hypothesised co-development of motor imagery and response inhibition abilities could be assessed by examining how novel actions are internalised in adults.\footnote{While keeping in mind the obvious limitation that the child mind is not equivalent to the adult mind, nor is it equivalent to a smaller version of the adult mind. Nevertheless, examining the development of novel imagined actions in adults avoids the contamination of the process of interest (imagined action) by developmental confounds.} For instance, Let’s consider the analogy between speaking and playing a music instrument (e.g., playing the piano). Essentially, learning to play the piano can be said to consist in learning to produce and coordinate complex and fine-grained motor sequences that in turn produce multisensory (e.g., kinaesthetic, auditory, visual) feedback to the agent producing of the action. Therefore, it appears that the act of speech can be paralleled with the act of playing an instrument as it consists in the coordination of complex movements that result in some modifications of the environment, that in turn generate sensory feedbacks (e.g., kinaesthetic, auditory) for the agent. This analogy suggests that we might be able to study the development of internal models responsible for the sensory experience accompanying imagined actions in the adult mind (e.g., when an individual is learning either a novel music instrument or a new language with speech sounds that are not present in his/her native language). By examining the development of novel imagined actions in the adult mind and by using motor interference (e.g., articulatory suppression) procedures, we might gain new insights about the internalisation of speech during childhood.

% \section{The interplay between motor control and cognition}

% \subsection{Where does this sensory content come from?}

% Where does the sensory content of covert verbal actions come from? How does motor learning shape these sensory percepts? In other words, how do the motor and perceptual system interact during covert speech? In the first subsection, we discuss two mechanisms that may be responsible for providing the sensory content of covert speech and their respective involvement in different forms of covert speech. In the second subsection, we discuss an exciting avenue for investigating the influence of motor learning on the sensory content of covert speech, namely, the imagery of totally novel (i.e., never executed) speech acts.

@@

% a theoretical account of the mechanisms leading to the generation of sensory percepts during covert speech production.

@@

% This is consistent with results from training studies suggesting that we rely more and more on domain-general (e.g., memory-based) processes with expertise \citep[e.g.,][]{tarr_mental_1989, jolicoeur_time_1985}.

% \subsection{The covert production of novel verbal actions}

% If, as suggested in the previous section, the sensory content of covert speech is, at least in some situations, provided by a motor simulation process, how can we imagine totally novel actions? Broadly speaking, the simulationnist framework suggests that the multisensory experience of motor imagery results from the simulation of the corresponding motor action, reusing internal models developed for the control of overt actions \citep[e.g.,][]{jeannerod_representing_1994}. In other words, internal models developed for the control of actions would then be used to simulate the sensory consequences of covert actions. Crucially, these internal models are generative models, which means that they can be used to compute or predict the sensory consequences of any action that can be parsed as a \citep[possibly supramodal, see][]{loevenbruck_cognitive_2018} goal to an inverse internal model. In other words, this framework makes it possible for novel actions to be simulated internally.\footnote{\cite{mulder_role_2004} assessed whether the mental practice of a totally novel movement (abduction of the big toe of the dominant right foot) resulted in better overt execution over the course of several weeks of practice. They observed that although mental practise did improve execution in the group of participants that already had some experience with the task at baseline, mental practise did not lead to statistically significant improvements in execution in the group of participants that had zero experience with the task at baseline. However, a Bayesian reanalysis of their results suggests that the evidence in favour of the null hypothesis was rather inconclusive ($\text{BF}_{01} = 1.92$, using a weakly informative Cauchy prior on the standardised effect size for the alternative hypothesis, with $r = 1$).}

% A general prediction of this framework is that the imagination of novel actions, and more precisely, the predicted sensory consequences of novel actions, may be "biased" or "constrained" by the repertoire of already-known actions. For instance, when asked to imagine playing table tennis, a tennis player may overestimate movements' amplitude and duration. Translated to speech production, this prediction could be assessed by asking participants to imagine a novel verbal action and subsequently checking whether this improves the execution of an "intermediate" novel action in the articulatory space. The same logic could be applied to the covert production of speech with someone else's voice. How can we imagine speaking with the voice of our relatives? If it is based on simulators, then the covert production of speech with someone else's voice should possess sensory properties that are somehow "biased" or "constrained" by the properties of our own sensory and motor systems. In other words, the subjective auditory sensation of covert speech with someone else's voice should be situated in a somehow intermediate (i.e., between the acoustic properties of our own voice and the acoustic properties of someone else voice) location in the auditory space.

% This prediction could be assessed experimentally by using the sensory attenuation effect observed during covert speech production. Auditory stimuli elicit an electrophysiological brain response with a characteristic N1 component. This N1 component has been shown to be reduced when the presentation of an auditory stimulus is synchronised with the self-production of a phonetically-matched vocalisation, an effect called N1-suppression. More interestingly, \cite{whitford_neurophysiological_2017} have shown that the covert production of a phoneme also resulted in sensory attenuation, as assessed by N1-suppression, when the content of the imagined phoneme matched the content of the audible phoneme. Therefore, we could describe the subjective auditory sensation of covertly speaking with someone else’s voice by manipulating the acoustic properties of the auditory stimulus that is presented to the participant to find the stimulus that produces the greatest sensory attenuation, as assessed by N1-suppression. In other words, sensory attenuation should be the strongest when it matches the auditory representation of the speaker. If the auditory percepts generated when covertly speaking with the voice of someone else is "constrained" by our own sensory and motor systems, then this point of greatest sensory attenuation should occur in an intermediate location in the feature space.

@@

% This led us to a discussion of two main themes. First, we asked how it is possible for covert speech production not to lead to overt speech production. Second, we discussed two mechanisms that may be used to provide the sensory content of covert speech, and how their respective involvement may be constrained by the available computational resources. To sketch an answer to these questions, we connected results from the motor imagery, motor inhibition, and covert speech research traditions.

We explored some of the theoretical and experimental consequences that emerge when considering covert speech production as inhibited overt speech production. To this end, we connected results from the motor imagery, motor inhibition, and covert speech domains. Regarding the role of general-purpose inhibitory mechanisms during the production of covert speech, we suggested that these may be similar to the inhibitory network responsible for proactive response inhibition and we summarised some propositions from this literature. We related the development of response inhibition abilities in childhood development with the purported internalisation of private speech around the same period. From the response inhibition perspective, the internalisation of speech from overt to covert speech may essentially be considered as "learning not to produce speech".

@@

% \color{blue}

% The Author Contributions section is mandatory for all articles, including articles by sole authors. If an appropriate statement is not provided on submission, a standard one will be inserted during the production process. The Author Contributions statement must describe the contributions of individual authors referred to by their initials and, in doing so, all authors agree to be accountable for the content of the work. Please see  \href{http://home.frontiersin.org/about/author-guidelines#AuthorandContributors}{here} for full authorship criteria.

% \color{black}

@@

% Details of all funding sources should be provided, including grant numbers if applicable. Please ensure to add all necessary funding information, as after publication this is no longer possible.

@@

\begin{figure}[ht] % float was h! initially
\begin{center}
\includegraphics[width=0.75\textwidth]{figures/inhibitory_triangle.png} % This is a *.eps file
\end{center}
\caption{Plausible implementation of the cortical and subcortical inhibitory mechanisms responsible for the "proactive" (but implicit) response inhibition at play during covert speech production. The pre-SMA, right IFC, and STN together form an \textit{inhibitory network} known as the \textit{inhibitory triangle}, which may be responsible for braking motor commands during covert speech production. Figure created with BioRender.com.}\label{fig:2}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Creates an explanation Box environment %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{Nalborczyk {et al.}} % use et al only if is more than 1 author
\def\Authors{Ladislas Nalborczyk\,$^{1,2,*}$, Ursula Debarnot\,$^{3,4}$, Marieke Longcamp\,$^{2}$, Aymeric Guillot\,$^{3,4}$, and F.-Xavier Alario\,$^{1}$}
% Affiliations should be keyed to the author's name with superscript numbers and be listed as follows: Laboratory, Institute, Department, Organization, City, State abbreviation (USA, Canada, Australia), and Country (without detailed address information such as city zip codes or street names).
% If one of the authors has a change of address, list the new address below the correspondence details using a superscript symbol and use the same symbol to indicate the author in the author list.
\def\Address{$^{1}$Aix Marseille Univ, CNRS, LPC, Marseille, France \\
$^{2}$Aix Marseille Univ, CNRS, LNC, Marseille, France \\
$^{3}$Inter-University Laboratory of Human Movement Biology-EA 7424, University of Lyon, University Claude Bernard Lyon 1, Villeurbanne, France \\
$^{4}$Institut Universitaire de France, Paris, France}
% The Corresponding Author should be marked with an asterisk
% Provide the exact contact address (this time including street name and city zip code) and email of the corresponding author
\def\corrAuthor{Ladislas Nalborczyk}
\def\corrEmail{ladislas.nalborczyk@univ-amu.fr}

@@

@@

@@

First and foremost, we need to make a distinction between at least two different types of inhibition: the inhibition of physical response (e.g., planning to raise the arm and finally not doing it), and cognitive inhibition, defined as "the stopping or overriding of a mental process, in whole or in part, with or without intention" \citep{gorfein_concept_2007}. Here, we are concerned with the former, which can be defined broadly as the withholding, suppression, or overriding of an inappropriate, prepotent, or unwanted motor response \citep{aron_neural_2007, oshea_go_2018}. \cite{ridderinkhof_dont_2014} further described the concept of response inhibition on three continuous dimensions: intentionality, premeditation, and specificity. Inhibition can be employed with more or less intentionality (intentional vs. reactive), planned ahead or employed in the moment (early vs. late inhibition), and applied to a specific action and effector, or more globally, that is, to all actions and/or effectors.

Crucially, we hypothesise that covert speech involves an intentional (we know we want to produce these actions covertly rather than overtly) but automatic (we do not explicitly think about not producing movements) and planned ahead form of response inhibition, which may apply both globally and in an effector-specific manner. Supporting the latter hypothesis, \cite{rieger_inhibition_2017} and \cite{bart_inhibitory_2021} have shown, using an action mode (overt vs. covert) switching paradigm, that the motor imagery of hand movements is accompanied by both global and effector-specific inhibition \citep[these results were also replicated in][]{scheil_motor_2018}. Notice however that the type of motor inhibition that may be at play during motor imagery is still different from the "proactive inhibition" in the motor inhibition literature. Indeed, in behavioural tasks aiming to assess proactive inhibition, participants are instructed not to execute an action. In contrast, while doing motor imagery,
participants are asked to produce the action \textit{covertly}, which implicitly implies that it should not be executed overtly \citep{guillot_imagining_2012}.

After reviewing evidence from electrophysiological, neuroimaging, and clinical studies, \cite{guillot_imagining_2012} suggested three possible routes whereby motor commands can be inhibited during motor imagery. First, motor inhibition can be integrated within the representation of the action to be produced internally, therefore no inhibition would be involved during motor imagery. Second, cerebral regions such as the supplementary motor area (SMA) \citep{kasess_suppressive_2008} or the right inferior frontal gyrus (rIFG) may weaken the motor commands that are emitted during motor imagery \citep[e.g.,][]{angelini_motor_2015, angelini_proactive_2016}, in addition to modulations of short-interval intracortical inhibition within the primary motor cortex itself \citep{neige_unravelling_2020}. More precisely, the pre-SMA and the rIFG may work together to intercept the action process via the basal ganglia (subthalamic nucleus, STN), hence suppressing the output from the basal ganglia which in turn might inhibit the primary motor cortex \citep{aron_reactive_2011} (cf. Figure \ref{fig:2}).\footnote{\cite{diesburg_pause-then-cancel_2021} proposed a functional dissociation between the pre-SMA and the rIFC in a two-stage "pause-then-cancel" model of action inhibition. In their model, they suggest that the pre-SMA would be involved in (globally) pausing the action whereas the rIFC would be involved in selectively cancelling (resetting) motor commands. Whether this functional dissociation is preserved in motor imagery and covert speech remains an open question.} Third, downstream regions in the cerebellum \citep[e.g.,][]{lotze_activation_1999}, in the brainstem \citep[e.g.,][]{jeannerod_neural_2001, jeannerod_motor_2006}, or at the spinal level may contribute to motor inhibition at a later stage.

@@

% \citep[e.g.,][]{angelini_motor_2015, angelini_proactive_2016}... \cite{ganos_action_2014} have showed that the behavioural performance during a stop-signal reaction-time task was similar across Tourette patients and healthy controls...

The role of inhibitory mechanisms during motor imagery and covert speech could be assessed in several ways. First, it could be assessed by experimentally manipulating the activity of the inhibitory network responsible for preventing execution during motor imagery. For instance, transcranial magnetic stimulation (TMS) could be used to "brake" these inhibitory mechanisms and "force" or facilitate execution during motor imagery. Second, the role of inhibitory mechanisms during covert verbal actions could be examined in a population with well-identified inhibitory deficits. For instance, Tourette syndrome is a childhood-onset neurological disorder affecting approximately 1\% of children and characterised by chronic motor and phonic tics \citep{jackson_inhibition_2015}. Verbal tics can consist of repeating sounds, words, or utterances (palilalia), producing inappropriate or obscene utterances (coprolalia), or the repetition of another’s words (echolalia). In their review, \cite{jackson_inhibition_2015} suggested that increased control over motor outputs is brought by local increases in GABAergic "tonic" inhibition within regions such as the SMA, leading to localised reductions in the gain of motor excitability. For these reasons, comparing the neural implementation of inhibitory mechanisms during covert speech in patients with Tourette syndrome and healthy controls may shed light on the role and flexibility of these mechanisms.

@@

\cite{watson_psychology_1919} suggested that thought (i.e., covert speech, in his terminology) was rooted in (overt) speech, that is, that covert speech matures from overt speech. \cite{vygotsky_thought_1934} further formulated the idea that covert speech originates from private egocentric speech, that is, self-addressed overt speech in childhood. In other words, Vygotsky observed, as Piaget before, that egocentric speech tends to be internalised during child development. \cite{fernyhough_alien_2004} extended this idea with four levels of internalisation: external dialogue, private speech, expanded inner speech, and condensed inner speech. These levels represent stages of development but also define movements between levels, that is, how we go from overt to covert speech and conversely. The level at which speech is expressed may depend on inhibitory control applied at different levels in the production flow, such as the formulation or the articulatory planning level \citep{grandchamp_condialint_2019}. Therefore, producing speech covertly crucially depends on successfully inhibiting speech production at several levels. We formulate the hypothesis that the progressive internalisation of speech during childhood may be related to the development of inhibitory abilities.

@@

Second, the hypothesised co-development of motor imagery and response inhibition abilities could be assessed by examining how novel actions are internalised in adults.\footnote{While keeping in mind the obvious limitation that the child mind is not equivalent to the adult mind, nor is it equivalent to a smaller version of the adult mind. Nevertheless, examining the development of novel imagined actions in adults avoids the contamination of the process of interest (imagined action) by developmental confounds.} For instance, let's consider the analogy between speaking and playing a music instrument (e.g., playing the piano). Essentially, learning to play the piano can be said to consist in learning to produce and coordinate complex and fine-grained motor sequences that in turn produce multisensory (e.g., kinaesthetic, auditory, visual) feedback to the agent producing of the action. Therefore, the act of producing speech can be paralleled with the act of playing an instrument as both actions consist in the coordination of complex movements that result in some modifications of the environment, that in turn generate sensory feedbacks (e.g., kinaesthetic, auditory) for the agent. This analogy suggests that we might be able to study the development of internal models responsible for the sensory experience accompanying imagined actions in the adult mind (e.g., when an individual is learning either a novel music instrument or a new language with speech sounds that are not present in his/her native language). By examining the development of novel imagined actions in the adult mind and by using motor interference (e.g., articulatory suppression) procedures, we might gain new insights about the internalisation of speech during childhood.

@@

@@

@@

We explored some of the theoretical and experimental consequences that emerge when considering covert speech production as inhibited overt speech production. To this end, we connected results from the motor imagery, motor inhibition, and covert speech domains. Regarding the role and implementation of general-purpose inhibitory mechanisms during the production of covert speech, we suggested that these may be similar to the inhibitory network responsible for proactive response inhibition and we summarised some propositions from this literature. We related the development of response inhibition abilities in childhood development with the purported internalisation of private speech around the same period. From the response inhibition perspective, the internalisation of speech from overt to covert speech may essentially be considered as "learning not to produce speech".

@@

@@

@@

\begin{figure}[ht] % float was h! initially
\begin{center}
\includegraphics[width=0.75\textwidth]{figures/inhibitory_triangle.png} % This is a *.eps file
\end{center}
\caption{Plausible implementation of the cortical and subcortical inhibitory mechanisms responsible for the "proactive" (but implicit) response inhibition at play during covert speech production. The pre-SMA, posterior rIFC, and STN together form an \textit{inhibitory network} known as the \textit{inhibitory triangle}, which may be responsible for braking motor commands during covert speech production. Figure created with BioRender.com.}\label{fig:2}
\end{figure}
